---
title: "Descriptive Finding Assignment"
author: "Manuel Wüthrich"
date: "4/20/2020"
output:
  pdf_document:
    latex_engine: xelatex
link-citations: yes
bibliography: descriptive_finding.bib

---

# Histogram of Government Types in 2017

This tiny descriptive research shows different government types among 36 OECD and/or EU-members in the year 2017 based on the comparative political data set (CPDS, @armingeon_2019). They describe seven different government types, however there were no caretaker or technocratic governments in 2017, so we focus only on five of them.

- 1 Single-party majority government: One party takes all governments seats and has a parliamentary majority [>50.0%].
- 2 Minimal winning coalition: All participating parties are necessary to form a majority government [>50.0%].
- 3 Surplus coalition: Coalition governments which exceed the minimal-winning criterion [>50.0%].
- 4 Single-party minority government: The party in government does not possess a majority in Parliament [≤50.0%].
- 5 Multi-party minority government: The parties in government do not possess a majority in Parliament [≤50.0%].

The following histogram shows how many countries have got a certain government type. Accordingly, we can say the most common government type among those 36 countries is a minimal winning coalition (2).


```{r, echo=FALSE}
# plot size

knitr::opts_chunk$set(fig.width=4, fig.height=3, fig.align = "center") 
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# packages

library(rio)
library(dplyr)
library(stargazer)
library(ggplot2)

# import data

data <- import("CPDS-1960-2017-Update-2019.xlsx")

# filter data

filtered.data <- data %>%             
  filter(year == "2017")   # limit it to observations from 2017

# visualise data
       
ggplot(data=filtered.data, aes(gov_type)) + 
geom_histogram(binwidth = 0.5,
               col="black",
               fill="grey") +
  labs(title="Histogram of Government Types in 2017",
       x="Government Types",
       y="Number of Countries") +
  scale_y_continuous(breaks = seq (0, 15, by = 1))
```